### 2011-08-11 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

\begin{itemize}
	\item For each input file: how long does model creation take?
	\item How long does it take to communicate with GLPK? Creating the input/parsing the output.
	\item Which construction heuristic is the best - limit GLPK to like 1 second
	\item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
	\item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Alpha, Beta -> How does the solution work?
	\item Which GLPK -> How does (time->quality) look, how does (input->time) look
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Fuzzy wins for every single case) - take note of quality (mean, variance) but also time (again, mean)
\end{itemize}

@@

TODO extension to more documents, IDREFs, ...

@@

>>>>

\begin{itemize}
	\item For each input file: how long does model creation take?
	\item How long does it take to communicate with GLPK? Creating the input/parsing the output.
	\item Which construction heuristic is the best - limit GLPK to like 1 second
	\item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
	\item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Alpha, Beta -> How does the solution work?
	\item Which GLPK -> How does (time->quality) look, how does (input->time) look
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Fuzzy wins in every single case) - take note of quality (mean, variance) but also time (again, mean)
  \item Can FIDAX be improved by Hungry?
\end{itemize}

@@

TODO

\begin{itemize}
  \item extension to more documents at once
  \item more heuristics and their chaining
  \item ACO, genetic, ...
  \item user-friendly experimental interface (choose and setup experiments on the fly in GUI)
  \item jInfer is opensource, thus easy to extend!
\end{itemize}

@@

TODO to the best of our knowledge, this framework is one-of-a-kind
